### 2022-06-07 src/text/3-applications-subsections/3D-analysis.tex
Reformat text files

\subsection{3D Analysis}
\label{ssec:3d-analysis}
\todo{Laura}
The 1D analysis approach is a powerful tool to measure the spectrum of an isolated source. However, more complicated situations require a more careful treatment. In fields of view containing several overlapping sources, the 1D approach can't disentangle the contribution of each source to the total flux in the selected region. Sources with extended or complex morphology can result in the measured flux being underestimated, and heavily dependent on the choice of extraction region. Additionally, the 1D approach neglects the energy-dependence of the PSF.

For such situations a more complex approach is needed, the so-called 3D analysis. The three relevant dimensions are the two spatial angular coordinates and an energy axis. In this framework, a combined spatial and spectral model (that is, a SkyModel, see Section~\ref{ssec:gammapy-modeling}) is fitted to the sky-maps that were previously derived from the data and bundled into a MapDataset (see Sections~\ref{ssec:gammapy-makers,ssec:gammapy-datasets}).

@@

As the example above shows, the 3D analysis allows to characterize the morphology of the emission and fit it together with the spectral properties of the source.  Among the advantages that this provides is the ability to disentangle the contribution from overlapping sources to the same spatial region. To highlight this, we define a circular RegionGeom of radius 0.5\textdegree centered around the position of the point source, which is drawn in the left panel of Figure~\ref{fig:cube_analysis}. We can now compare the measured excess counts integrated in that region to the expected relative contribution from each of the three source models. This can be seen in the left panel of Figure~\ref{fig:cube_analysis}.

@@

Note that all the models fitted also have a spectral component, from which flux points can be derived in a similar way as described in~\ref{ssec:1d-analysis}.
%
%\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?
%Ref:~\citep{Stewart2009} \begin{figure*}[t] \centering
%	\includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}
%	\caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}
%\end{figure*}

>>>>

\subsection{3D Analysis}
\label{ssec:3d-analysis}
\todo{Laura}
The 1D analysis approach is a powerful tool to measure the spectrum of an
isolated source. However, more complicated situations require a more careful
treatment. In a field of view containing several overlapping sources, the 1D
approach can't disentangle the contribution of each source to the total flux in
the selected region. Sources with extended or complex morphology can result in
the measured flux being underestimated, and heavily dependent on the choice of
extraction region. Additionally, the 1D approach neglects the energy-dependence
of the PSF.

For such situations a more complex approach is needed, the so-called 3D
analysis. The three relevant dimensions are the two spatial angular coordinates
and an energy axis. In this framework, a combined spatial and spectral model
(that is, a SkyModel, see Section~\ref{ssec:gammapy-modeling}) is fitted to the
sky-maps that were previously derived from the data and bundled into a
MapDataset (see Sections~\ref{ssec:gammapy-makers} and~\ref{ssec:gammapy-datasets}).

@@

As the example above shows, the 3D analysis allows to characterize the
morphology of the emission and fit it together with the spectral properties of
the source.  Among the advantages that this provides is the ability to
disentangle the contribution from overlapping sources to the same spatial
region. To highlight this, we define a circular RegionGeom of radius
0.5\textdegree~ centered around the position of the point source, which is drawn
in the left panel of Figure~\ref{fig:cube_analysis}. We can now compare the
measured excess counts integrated in that region to the expected relative
contribution from each of the three source models. The result can be seen in the left
panel of Figure~\ref{fig:cube_analysis}.

@@

Note that all the models fitted also have a spectral component, from which flux
points can be derived in a similar way as described in~\ref{ssec:1d-analysis}.
%\end{figure*}%	\caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}%	\includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}%Ref:~\citep{Stewart2009} \begin{figure*}[t] \centering%\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?%
